Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
structural edits

## Analysis

### Mean Education Level from 2000 - 2021

@@

### Mean Occupational Prestige from 2000 - 2021

@@

### Women's Happiness from 2000 - 2021

@@

Figure 1 shows an increase in mean highest education level, Figure 2 shows an increase in mean occupational prestige percentage and Figure 3 shows an increase in overall happiness. This means that at a slow and steady rate, women are acquiring better education, getting better jobs and becoming happier. The findings show that there is a positive relationship between job prestige, education and happiness. Just do these three factors tie into one another?

@@

According to the UNICEF (citation), the education of girls enhances economies and mitigates inequality, promoting more stable and resilient societies that offer all individuals, including boys and men, the chance to reach their full potential.Over the past two decades, there has been a steady increase in women's education levels, as evidenced by Figure 1, which displays a positive upward trajectory in women's education levels over time. This trend can be attributed to several factors.\

@@

One factor is the state of the economy [@citeTBC], as the increase in female education can be partly attributed to the rise in female employment rates. As the demand for skilled labor increases with economic growth, women's education becomes a more valuable asset in the labor market, leading to higher employment rates for women. Families also recognize the long-term benefits of investing in girls' education, prioritizing it over time. However, there can be volatility in education levels due to the state of the economy, as seen in the decline from 2004 to 2006 in figure 1. This could be seen as the volatility of the state of economy, and its relationship with the labor market and opportunities. In periods when the employment rate increases, Families are more likely to invest in girls\' education because education offers benefits in the labor market. Educated women are more likely to have higher-paying jobs, leading to better financial stability for themselves and their families. This is one of the economic forces that contribute to the rise in female education over the past two decades.

>>>>

## Mean Education Level from 2000 - 2021

@@

## Mean Occupational Prestige from 2000 - 2021

@@

## Women's Happiness from 2000 - 2021

@@

Figure 1 shows an increase in mean highest education level, Figure 2 shows an increase in mean occupational prestige percentage and Figure 3 shows an increase in overall happiness. This means that at a slow and steady rate, women are acquiring better education, getting better jobs and becoming happier. The findings show that there is a positive relationship between job prestige, education and happiness.

@@

According to the UNICEF (citation), the education of girls enhances economies and mitigates inequality, promoting more stable and resilient societies that offer all individuals, including boys and men, the chance to reach their full potential.Over the past two decades, there has been a steady increase in women's education levels, as evidenced by Figure 1, which displays a positive upward trajectory in women's education levels over time. This trend can be attributed to several factors.

@@

One factor is the state of the economy [@citeTBC], as the increase in female education can be partly attributed to the rise in female employment rates. As the demand for skilled labor increases with economic growth, women's education becomes a more valuable asset in the labor market, leading to higher employment rates for women. Families also recognize the long-term benefits of investing in girls' education, prioritizing it over time. However, there can be volatility in education levels due to the state of the economy, as seen in the decline from 2004 to 2006 in @fig-1. This could be seen as the volatility of the state of economy, and its relationship with the labor market and opportunities. In periods when the employment rate increases, Families are more likely to invest in girls\' education because education offers benefits in the labor market. Educated women are more likely to have higher-paying jobs, leading to better financial stability for themselves and their families. This is one of the economic forces that contribute to the rise in female education over the past two decades.
